The K2 Bright Star Survey I: Methodology and Data Release

### 2019-07-15 paper/ms.tex
refer to figures in the text

We calculated halo light curves of 36\,Oph and their CDPPs for $k \in \{1,2,3\}$, and $\delta \in [1,50]$ for long cadence and for various valies of $\delta \in [1,2500]$ for short cadence data. The results are displayed in Figures~\ref{cdpps_lc} and~\ref{cdpps_sc}. We found that for long cadence data, $k=1$ (TV) and a lag $\delta=10$ provide the best CDPP. As this is one cadence shorter than the 12~cadence thruster firing period, we can understand the optimum as suppressing systematics on the same timescale as they occur. On the other hand, for short cadence data, performance at short lags is very poor but the method performs similarly for $k \in \{1,2\}$ with slow improvement with larger $\delta$, and performs very poorly for $k=3$ at all lags.

@@

The blue supergiant $\rho$~Leonis, observed in Campaign~14, was studied with halo photometry but without the TV-min method by \citet{Aerts2018}. In that reduction, \citet{Aerts2018} used four different aperture masks to extract raw light curves, and detrended these for K2 systematics with \textsc{k2sc} and a polynomial to account for long-term drift. They detected photometric variability at the star's rotation period of 26.8~d and also multiperiodic low-frequency variability ($<1.5 \text{d}^{-1}$). There is excellent agreement between the light curves produced by both methods. It is easiest to compare the methods in the power-spectral domain, where we see a reduction of only a few percent in the amplitude of oscillations in the TV-min and the \citet{Aerts2018} lightcurve; at high frequencies, both methods show significant residual systematics at the K2~thruster-firing frequencies, but the TV-min lightcurve shows a lower white noise floor by a factor of $\sim 3$.

>>>>

We calculated halo light curves of 36\,Oph and their CDPPs for $k \in \{1,2,3\}$, and $\delta \in [1,50]$ for long cadence and for various values of $\delta \in [1,2500]$ for short cadence data. The results are displayed in Figures~\ref{cdpps_lc} and~\ref{cdpps_sc}. We found that for long cadence data, $k=1$ (TV) and a lag $\delta=10$ provide the best CDPP. As this is one cadence shorter than the 12~cadence thruster firing period, we can understand the optimum as suppressing systematics on the same timescale as they occur. On the other hand, for short cadence data, performance at short lags is very poor but the method performs similarly for $k \in \{1,2\}$ with slow improvement with larger $\delta$, and performs very poorly for $k=3$ at all lags.

@@

The blue supergiant $\rho$~Leonis, observed in Campaign~14, was studied with halo photometry but without the TV-min method by \citet{Aerts2018}. In that reduction, \citet{Aerts2018} used four different aperture masks to extract raw light curves, and detrended these for K2 systematics with \textsc{k2sc} and a polynomial to account for long-term drift. They detected photometric variability at the star's rotation period of 26.8~d and also multiperiodic low-frequency variability ($<1.5 \text{d}^{-1}$). The \textsc{k2sc} systematics and variability models, residuals, halo apertures, and periodograms are shown in Figure~\ref{fig:rholeo}, and a comparison with the \citet{Aerts2018} lightcurve in Figure~\ref{rholeo_comparison}. There is excellent agreement between the light curves produced by both methods. It is easiest to compare the methods in the power-spectral domain, where we see a reduction of only a few percent in the amplitude of oscillations in the TV-min and the \citet{Aerts2018} lightcurve; at high frequencies, both methods show significant residual systematics at the K2~thruster-firing frequencies, but the TV-min lightcurve shows a lower white noise floor by a factor of $\sim 3$.
